stats-project

### 2020-12-05 R - Deliverable/MSDS 6371 - Project.Rmd
Changes on the custom model

final_custom_test_data$KitchenQual = as.character(final_custom_test_data$KitchenQual)
final_custom_test_data = custom_test_data %>%   mutate_at(vars(KitchenQual) ,     ~ifelse(is.na(.x),"Ex",.x  ))
final_custom_test_data$KitchenQual = as.factor(final_custom_test_data$KitchenQual)

@@

custom_predictions2 = c(predict(custom_model2, newdata = one_encode_custom_test_data2))
custom_predictions2

custom_predictions2 = data.frame(Id= one_encode_custom_test_data2$Id, SalePrice=custom_predictions2)
custom_predictions2
write_csv(custom_predictions2, "../kaggleData/customSelection2Predictions.csv")
```

>>>>

final_custom_test_data$KitchenQual = as.character(final_custom_test_data$KitchenQual)
final_custom_test_data = final_custom_test_data %>%   mutate_at(vars(KitchenQual) ,     ~ifelse(is.na(.x),"Ex",.x  ))
final_custom_test_data$KitchenQual = as.factor(final_custom_test_data$KitchenQual)

@@

custom_predictions2 = c(predict(custom_model2, newdata = one_encode_custom_test_data2))

custom_predictions2 = data.frame(Id= one_encode_custom_test_data2$Id, SalePrice=custom_predictions2)
custom_predictions2
write_csv(custom_predictions2, "../kaggleData/customSelection2Predictions.csv")
```
```{r}
one_encode_custom_test_data2
```
```{r}
custom_model2
